---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

## Step 1

Inspect first few lines of dataset:

```{r}
library(classdata)
head(ames)
```
The different variables are Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale (if the sale was a package deal), Year Built, Acres, TotalLivingArea (sf), Bedrooms, FinishedBsmtArea (sf), LotArea (sf), AC (if the property has AC), FirePlace (if the property has a fireplace), and Neighborhood.

The type of variable and their data range can be pictured with summary(ames):
```{r}
summary(ames)
```

## Step 2

The variable of interest is Sale Price.

## Step 3

Draw histogram of Sale Price:
```{r}
library(ggplot2)
ggplot(ames, aes(`Sale Price`)) +
  geom_histogram(binwidth = 50000)
```

## Step 4


Kylie: TotalLivingArea

```{r}
ggplot(ames, aes(`TotalLivingArea (sf)`)) +
  geom_histogram(binwidth = 100, na.rm = TRUE)
```

Lucas:

Aiden:
